Essays in \\Computational Management Science

### 2018-05-11 Chapters/Chapter01.tex
Hathor: conclusion and minor fixes.

\chapter{Analysis of Bitcoin}
\input{./Chapters/hathor-bitcoin-math.tex}

@@

Today, Bitcoin network can barely handle 8 transactions per second without increasing the unconfirmed transaction list to hundreds of thousands --- several transactions take days to be confirmed. In order to increase Bitcoin's capacity, its community has first proposed and implemented segregated witness, which was not enough. Finally, they proposed the lightning network, which is in development and should be available in the next months. I believe these proposals relieve the network---a temporary solution---, but do not solve the scalability problem.

Hathor's architecture allows a great number of transactions per second, since new transactions confirm previous ones (and there is no such thing as ``maximum block size''). The more transactions are coming, the faster previous transactions will be confirmed. It is the opposite of Bitcoin because the network benefits from high volume scenarios.

As the transactions also have a proof-of-work, it becomes harder to performan a spam attack. The attacker would spend a considerable amount of computational resources to solve the proof-of-work of all transactions. The amount of work depends on the transaction's weight. Future work may explore automatic adjustments in transaction's weight to improve spam prevention. For instance, the network can detect a high number of new transactions coming and increase the transaction's weight for a while. Or else, the transaction's weight may be a function of the time between an output and its spending transaction, so, transferring the same tokens over and over in a small window of time would require a higher weight.

>>>>

\chapter{Analysis of Bitcoin}
\label{ch:hathor-bitcoin-math}
\input{./Chapters/hathor-bitcoin-math.tex}

@@

Today, Bitcoin network can barely handle 8 transactions per second without increasing the unconfirmed transaction list to hundreds of thousands --- several transactions take days to be confirmed. In order to increase Bitcoin's capacity, its community has first proposed and implemented segregated witness, which improved scalability yet was not enough. Finally, they proposed the lightning network, which is in development and should be available in the next months. I believe these proposals relieve the network---a temporary solution---, but do not solve the scalability problem.

Hathor's architecture allows a great number of transactions per second, since new transactions confirm previous ones (and there is no such thing as ``maximum block size''). The more transactions are coming, the faster previous transactions will be confirmed. It is the opposite of Bitcoin because the network benefits from high volume scenarios. As I have shown, Hathor seems to solve the scalability problem present in Blockchain-based cryptocurrencies.

As the transactions also have a proof-of-work, it becomes harder to perform a spam attack. The attacker would spend a considerable amount of computational resources to solve the proof-of-work of every transaction, and the amount of work depends on the transaction's weight parameter. Future work may explore automatic adjustments in transaction's weight to improve spam prevention. For instance, the network can detect a higher number of new transactions coming and increase the transaction's weight for a while. Or else, the transaction's weight may be a function of the time between an output being spent and its spending transaction, so, transferring the same tokens over and over in a small window of time would require more work. Anyway, the transaction's weight seems to tackle the spam issue. The new challenge is to set a proper transaction's weight which would prevent spam without impairing IoT devices.

The last, but not least, challenge is the hashpower centralization. Although Bitcoin seems to have the most decentralized network among cryptocurrencies, there are few miners and mining pools which together control over 50\% of the network’s computing (hash)power \citep{gencer2018decentralization}. Hence, they have an oversized influence when it comes to changes in the Bitcoin protocol's behavior. Hathor's architecture splits the hashpower among miners and users. Even if miners have more individual hashpower than users, because they would have rigs with appropriate cooling and energy supply, I believe their aggregate hashpower will not surpass users' aggregate hashpower when millions of devices are generating transactions. Future IoT devices may even come with an application-specific integrated circuit (asic) designed to solve Hathor's proof-of-work without spending too much battery. Future work may check common IoT processors' hashpower, which would allows us to estimate how many devices would be necessary to surpass miners' hashpower.

Even though I have proposed to update block's weight every 24 hours (or 675 blocks), this was an arbitrary number. Future work may explore whether it would be feasible to continuously update block's weight, or what would be the optimal number of blocks between each update. I believe that the challenge of a continuous update approach would be preventing outdated nodes to discard valid blocks when two or more blocks were being propagated through Hathor's network. Maybe a solution would be allowing a range of block's weight instead of a single value, but future work would have to check whether this can be exploited by attackers.

I also presented a mathematical analysis of Blockchain, going though mining, hashpower change, orphan blocks, and double-spending attacks. Most of the presented results may directly be applied to Hathor's blocks, since their foundations are the same. As \citet{tangle2016} has already analyzed Tangle, I have just applied their results with a few extensions.

Future work may also further analyze other possibilities of attack in Hathor's network, such as malicious device not using random tip selection. Another major challenge affecting all cryptocurrencies is disk space use. How would one wipe out part of the blocks and transactions without putting security in risk? At first, all blocks and transactions are required to check whether anyone (including computer viruses) has tampered with transactions which had already been validated and stored in disk.

### 2018-05-11 Chapters/hathor-architecture.tex
Hathor: conclusion and minor fixes.

In Bitcoin, it is well-known that one should wait at least ``six confirmations'' before accepting a transaction. This Bitcoin's criteria is based on some math presented in Satoshi's seminal work \citep{nakamoto2008bitcoin}. Adopting six confirmations is the same as demanding from attackers a minimal effort of six times the network's hash rate to successfully double spend those tokens. Let $H$ be the total hash rate of the network. Then, as $\mathbf{E}(Y_6) = 60 \text{ minutes}$, it will be necessary to calculate, on average, $\mathbf{E}(Y_6) \cdot H = 60 \cdot 60 \cdot H$ hashes to solve the proof-of-work of 6 blocks.

@@

For the blocks, $\eta = 128$, thus, $\mathbf{E}(T) = 128 \text{ seconds}$, and $\mathbf{V}(T) = 16,384$. The symmetrical confidence interval with $\alpha = 10\%$ is $[6.56, 383.45]$, i.e., 90\% of the cases the distance between blocks will be between 6 seconds and just under 7 minutes.

@@

This weight will be updated every 2,016 blocks to take into consideration the change of $H$. First, $H$ will be estimated using the fact that $\mathbf{E}(Y_{2016}) = \frac{2016}{\lambda} = 2016 \eta = \frac{2016}{pH} = \frac{2016 \cdot 2^w}{H}$. Thus, $H = \frac{2016 \cdot 2^w}{\Delta t} \Rightarrow \log_2(H) = w + \log_2(2016) - \log_2(\Delta t)$, where $\Delta t$ is the time between the latest weight update and now. Finally,

>>>>

In Bitcoin, it is well-known that one should wait at least ``six confirmations'' before accepting a transaction. This Bitcoin's criteria is based on some results presented in Satoshi's seminal work \citep{nakamoto2008bitcoin} and derived here in more detail in Chapter \ref{ch:hathor-bitcoin-math}. Adopting six confirmations is the same as demanding from attackers a minimal effort of six times the network's hash rate to successfully double spend those tokens. Let $H$ be the total hash rate of the network. Then, as $\mathbf{E}(Y_6) = 60 \text{ minutes}$, it will be necessary to calculate, on average, $\mathbf{E}(Y_6) \cdot H = 60 \cdot 60 \cdot H$ hashes to solve the proof-of-work of 6 blocks.

@@

For the blocks, $\eta = 128$, thus, $\mathbf{E}(T) = \eta = 128 \text{ seconds}$, and $\mathbf{V}(T) = \eta^2 = 16,384$, where $T$ is the random variable of the time between two consecutive blocks. The symmetrical confidence interval of $T$ with $\alpha = 10\%$ is $[6.56, 383.45]$, i.e., 90\% of the cases the distance between blocks will be between 6 seconds and just under 7 minutes.

@@

This weight will be updated every 675 blocks (which should happen every 24 hours) to take into consideration the change of $H$. First, $H$ will be estimated using the fact that $\mathbf{E}(Y_{2016}) = \frac{2016}{\lambda} = 2016 \eta = \frac{2016}{pH} = \frac{2016 \cdot 2^w}{H}$. Thus, $H = \frac{2016 \cdot 2^w}{\Delta t} \Rightarrow \log_2(H) = w + \log_2(2016) - \log_2(\Delta t)$, where $\Delta t$ is the time between the latest weight update and now. Finally,

### 2018-05-11 FrontBackmatter/Acknowledgments.tex
Hathor: conclusion and minor fixes.

Thanks to my wife, Patrícia, for sharing the dreams, the passion, and the craziness, for all her caring and love. Especially, for understanding my absence and my unusual working times. Her loyalty and commitment make me the luckiest man alive. I love you.

@@

Thanks to my friends Layla Mendes, Renato Kogeyama, André Luiz, Luiz Sacramento, Kaillen Givigi, Jamil Chivitarese, Lucia Barros, Daniel Modenesi, Bernardo Machado, and Andréia Sodré, always available for serious talking, laughing, and sharing their wide and deep knowledge, even at lunchtime and weekends. I will never forget our all-you-can-eat adventures in Bros restaurant, the snacks in Catarina, and the drinks in Bigode's bar. You have become close friends who I will carry for life.

>>>>

Thanks to my wife, Patrícia, for sharing the dreams, the passion, and the craziness, for all her caring and love. Especially, for understanding my absence and my unusual working times. Her loyalty and commitment make me the luckiest man alive. I love you, Xu.

@@

Thanks to my friends Daniel Chada, Layla Mendes, Renato Kogeyama, André Luiz, Luiz Sacramento, Kaillen Givigi, Jamil Chivitarese, Lucia Barros, Daniel Modenesi, Bernardo Machado, and Andréia Sodré, always available for serious talking, laughing, and sharing their wide and deep knowledge, even at lunchtime and weekends. I will never forget our all-you-can-eat adventures in Bros restaurant, the snacks in Catarina, and the drinks in Bigode's bar. You have become very close friends who I will carry for life.
